---
title: "Reverse primer too quickly"
output: html_notebook
---

### Cutadapt

Cutadapt offers an option to trim Fwd and Rev primers at once, with the syntax FWD...REV

The problem is that it often results in trimming the amplicon too short. This is painfully true with rRNA, because homologue regions do appear

This is how they look now

```{r, echo = F, message=F}
library (tidyverse)
```

I used `awk` to print to a file all sequences lengths

```{r, eval=F}
awk 'NR %4==2 {print length}' <path/with/wildcards/to/demult/files> > seq.lengths.demult.txt

awk 'NR %4==2 {print length}' <path/with/wildcards/to/noprimers/files> > seq.lengths.noprimers.txt

```



```{r current situation}
old.output <- "~/Documents/test_demult/demultiplexed_20220823_1422/"

read_table(file.path(old.output, "seq.lengths.demult.txt"), col_names = "len") %>%
  mutate(Step = "demult") %>% 
  bind_rows(read_table(file.path(old.output, "seq.lengths.noprimers.txt"), col_names = "len") %>%
  mutate(Step = "noprimers")) %>% 
  ggplot()+
  geom_density(aes(len, after_stat(count), fill = Step)) 
```

So the current set up cuts short in two ways

## First attempt: Increase the stringency of the last `cutadapt`. Start with 0.2 and 0.1


```{r stringency at 0.2 and 0.1}
output.0.2 <- "~/Documents/test_demult/demultiplexed_20220823_1453/"

read_table(file.path(output.0.2, "seq.lengths.demult.txt"), col_names = "len") %>%
  mutate(Step = "demult") %>% 
  bind_rows(read_table(file.path(output.0.2, "seq.lengths.noprimers.txt"), col_names = "len") %>%
  mutate(Step = "noprimers")) %>% 
  ggplot()+
  geom_density(aes(len, after_stat(count), fill = Step)) 
```
